---
title: "repeat_vaccine_effects"
author: "Tanmayi Patharkar"
date: "`r Sys.Date()`"
output: html_document
---
#Packages
```{r}
library(librarian)
shelf(dplyr,
      tidyverse,
      readxl, 
      tidyr, 
      rlang, 
      patchwork,
      ggplot2
      )
```

#Load whole data
```{r}
data <- read.csv("./data/20251007_hcw_posvax_abwaning.csv")

#Smaller Data Subset
subset_data <- data %>% select(-c(r11_svnt_ba5, r3_svnt_ba5, r4_svnt_ba5, r5_svnt_ba5, r6_svnt_ba5, r7_svnt_ba5, r8_svnt_ba5, r9_svnt_ba5, r10_svnt_ba5, r1_svnt_ba5, r2_svnt_ba5 #,v1_svnt_ba5, v2_svnt_ba5, v3_svnt_ba5, v4_svnt_ba5, v5_svnt_ba5, v6_svnt_ba5, v7_svnt_ba5, v8_svnt_ba5
                                  ))

#Add Permutations
subset_data <- subset_data %>%
  mutate(across(contains("date"), \(x) as.Date(x, format = "%Y-%m-%d"))) %>%
  mutate(
    one_dose_permutation = paste(dose1_brand),
    two_dose_permutation = paste(dose1_brand, dose2_brand, sep = "-"),
    three_dose_permutation = paste(dose1_brand, dose2_brand, dose3_brand, sep = "-"),
    four_dose_permutation = paste(dose1_brand, dose2_brand, dose3_brand, dose4_brand, sep = "-"),
    five_dose_permutation = paste(dose1_brand, dose2_brand, dose3_brand, dose4_brand, dose5_brand, sep = "-")
  )
```

#Source Functions
```{r}
#Source Baseline Value Measurements Function 
source("scripts/helper/fc_get_baselines.R")

#Yearly Snapshot Function Source
source("scripts/helper/fc_snapshot.R")
```

## Make Data Frames 

#Snapshots 2022
```{r}
snapshot_2022 <- snapshot_vaccine_year(subset_data, "2022-01-01")

svnt_snapshot_2022 <- calculate_titer(snapshot_2022, "_svnt_wt")
elisa_snapshot_2022 <- calculate_titer(snapshot_2022, "_elisa_wt")
```

#Snapshots 2021
```{r}
snapshot_2021 <- snapshot_vaccine_year(subset_data, "2021-08-01")
svnt_snapshot_2021 <- calculate_titer_3(snapshot_2021, "_svnt_wt")
elisa_snapshot_2021 <- calculate_titer(snapshot_2021, "_elisa_wt")
```

#mrna only svnt 2022
```{r}
mrna_svnt_snapshot_2022_test <- svnt_snapshot_2022 %>%
  filter(
    (is.na(dose1_brand) | dose1_brand == 1) &
    (is.na(dose2_brand) | dose2_brand == 1) &
    (is.na(dose3_brand) | dose3_brand == 1) &
    (is.na(dose4_brand) | dose4_brand == 1) &
    (is.na(dose5_brand) | dose5_brand == 1) 
  ) %>% filter(num_vaccines != 1) 

mrna_elisa_snapshot_2022_test <- elisa_snapshot_2022 %>%
  filter(
    (is.na(dose1_brand) | dose1_brand == 1) &
    (is.na(dose2_brand) | dose2_brand == 1) &
    (is.na(dose3_brand) | dose3_brand == 1) &
    (is.na(dose4_brand) | dose4_brand == 1) &
    (is.na(dose5_brand) | dose5_brand == 1) 
  ) %>% filter(num_vaccines != 1) 

mrna_svnt_long_2022 <- create_long_titer_data(mrna_svnt_snapshot_2022_test) %>% filter(time_point %in% c("Baseline", "Step 1"))
mrna_elisa_long_2022 <- create_long_titer_data(mrna_elisa_snapshot_2022_test) #%>% filter(time_point %in% c("Baseline", "Step 1"))
```

#inactivated only svnt 2022
```{r}
inact_svnt_snapshot_2022_test <- svnt_snapshot_2022 %>%
  filter(
    (is.na(dose1_brand) | dose1_brand == 4) &
    (is.na(dose2_brand) | dose2_brand == 4) &
    (is.na(dose3_brand) | dose3_brand == 4) &
    (is.na(dose4_brand) | dose4_brand == 4) &
    (is.na(dose5_brand) | dose5_brand == 4) #dose 5 can be omicron 
  ) %>% filter(num_vaccines != 1)

inact_elisa_snapshot_2022_test <- elisa_snapshot_2022 %>%
  filter(
    (is.na(dose1_brand) | dose1_brand == 4) &
    (is.na(dose2_brand) | dose2_brand == 4) &
    (is.na(dose3_brand) | dose3_brand == 4) &
    (is.na(dose4_brand) | dose4_brand == 4) &
    (is.na(dose5_brand) | dose5_brand == 4) #dose 5 can be omicron 
  ) %>% filter(num_vaccines != 1)

inact_svnt_long_2022 <- create_long_titer_data(inact_svnt_snapshot_2022_test) #%>% filter(time_point %in% c("Baseline", "Step 1"))
inact_elisa_long_2022 <- create_long_titer_data(inact_elisa_snapshot_2022_test) #%>% filter(time_point %in% c("Baseline", "Step 1"))
```

#mrna only svnt 2021
```{r}
mrna_svnt_snapshot_2021_test <- svnt_snapshot_2021 %>%
  filter(
    (is.na(dose1_brand) | dose1_brand == 1) &
    (is.na(dose2_brand) | dose2_brand == 1) &
    (is.na(dose3_brand) | dose3_brand == 1) &
    (is.na(dose4_brand) | dose4_brand == 1) &
    (is.na(dose5_brand) | dose5_brand == 1)
  ) 

mrna_elisa_snapshot_2021_test <- elisa_snapshot_2021 %>%
  filter(
    (is.na(dose1_brand) | dose1_brand == 1) &
    (is.na(dose2_brand) | dose2_brand == 1) &
    (is.na(dose3_brand) | dose3_brand == 1) &
    (is.na(dose4_brand) | dose4_brand == 1) &
    (is.na(dose5_brand) | dose5_brand == 1)
  ) 

mrna_svnt_long_2021 <- create_long_titer_data(mrna_svnt_snapshot_2021_test)
mrna_elisa_long_2021 <- create_long_titer_data(mrna_elisa_snapshot_2021_test)
```

#inactivated only svnt 2021
```{r}
inact_svnt_snapshot_2021_test <- svnt_snapshot_2021 %>%
  filter(
    (is.na(dose1_brand) | dose1_brand == 4) &
    (is.na(dose2_brand) | dose2_brand == 4) &
    (is.na(dose3_brand) | dose3_brand == 4) &
    (is.na(dose4_brand) | dose4_brand == 4) &
    (is.na(dose5_brand) | dose5_brand == 4)
  ) 

inact_elisa_snapshot_2021_test <- elisa_snapshot_2021 %>%
  filter(
    (is.na(dose1_brand) | dose1_brand == 4) &
    (is.na(dose2_brand) | dose2_brand == 4) &
    (is.na(dose3_brand) | dose3_brand == 4) &
    (is.na(dose4_brand) | dose4_brand == 4) &
    (is.na(dose5_brand) | dose5_brand == 4)
  )

inact_svnt_long_2021 <- create_long_titer_data(inact_svnt_snapshot_2021_test)
inact_elisa_long_2021 <- create_long_titer_data(inact_elisa_snapshot_2021_test)
```

################################################################################

#Make Plots 2022 Main

# sVNT 2022 Main 
```{r,warning=FALSE}
vaccine_colors <- c("1" = "darkred", "2" = "darkblue", "3" = "darkgreen")

mrna_plot_svnt_2022 <- ggplot(mrna_svnt_long_2022, aes(x = time_point, y = titer_value, 
                                                  color = as.factor(num_vaccines), 
                                                  fill = as.factor(num_vaccines))) +
  geom_point(alpha = 0.2, position = position_jitterdodge(jitter.width = 0.15, 
                                              dodge.width = 0.8,
                                              seed = 123),
             size = 2, alpha = 0.5) +
  geom_smooth(aes(group = as.factor(num_vaccines)),
              method = "lm",
              se = TRUE,
              alpha = 0.2,
              size = 1.2) +
  # Mean points
  stat_summary(aes(group = as.factor(num_vaccines)),
               fun = mean,
               geom = "point",
               size = 4,
               position = position_dodge(width = 0.8)) +
  scale_color_manual(values = vaccine_colors, name = "Number of\nVaccines") +
  scale_fill_manual(values = vaccine_colors, name = "Number of\nVaccines") +
  scale_y_continuous(breaks = seq(90, 100, by = 2),
                     limits = c(90, 100),
                     expand = c(0, 0)) +
  labs(x = "Time Point", 
       y = "sVNT (%)",
       color = "Number of\nVaccines",
       fill = "Number of\nVaccines",
       title = "mRNA (2022)") +
  theme_classic(base_size = 14) +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold", size = 16),
    plot.subtitle = element_text(hjust = 0.5, size = 12, color = "gray30"),
    legend.position = "none",
    legend.title = element_text(face = "bold"),
    axis.text.x = element_text(angle = 0, size = 12),
    axis.text.y = element_text(size = 12),
    axis.title = element_text(face = "bold"),
    panel.grid.major = element_line(color = "gray90", size = 0.2),
    panel.grid.minor = element_blank()
  )

inact_plot_svnt_2022 <- ggplot(inact_svnt_long_2022, aes(x = time_point, y = titer_value, 
                                                    color = as.factor(num_vaccines), 
                                                    fill = as.factor(num_vaccines))) + 
  geom_point(alpha = 0.2, position = position_jitterdodge(jitter.width = 0.15, 
                                              dodge.width = 0.8,
                                              seed = 145),
             size = 2, alpha = 0.5) +
  geom_smooth(aes(group = as.factor(num_vaccines)),
              method = "loess",
              se = TRUE,
              alpha = 0.2,
              size = 1.2) +
  # Mean points
  stat_summary(aes(group = as.factor(num_vaccines)),
               fun = mean,
               geom = "point",
               size = 4,
               position = position_dodge(width = 0.8)) +
  scale_color_manual(values = vaccine_colors, name = "Baseline \nVaccine") +
  scale_fill_manual(values = vaccine_colors, name = "Baseline \nVaccine") +
  scale_y_continuous(breaks = seq(0, 100, by = 10),
                     expand = c(0, 0)) +
  coord_cartesian(ylim = c(50, 105)) +  
  labs(x = "Time Point", 
       y = "sVNT (%)",
       color = "Baseline \nVaccine",
       fill = "Baseline \nVaccine", 
       title = "Inactivated (2022)") +
  theme_classic(base_size = 14) +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold", size = 16),
    plot.subtitle = element_text(hjust = 0.5, size = 12, color = "gray30"),
    legend.position = "right",
    legend.title = element_text(face = "bold"),
    axis.text.x = element_text(angle = 0, size = 12),
    axis.text.y = element_text(size = 12),
    axis.title = element_text(face = "bold"),
    panel.grid.major = element_line(color = "gray90", size = 0.2),
    panel.grid.minor = element_blank()
  )
```

#Print SVNT 2022 PLOT Both Main
```{r,warning=FALSE}
combined_plot_2022_svnt <- mrna_plot_svnt_2022 + inact_plot_svnt_2022 + 
  plot_annotation(
    tag_levels = "A",
    title = "Excluding Omicron"
  ) +
  plot_layout(guides = "collect") 

print(combined_plot_2022_svnt)

ggsave(
  filename = "combined_plot_2022_svnt.pdf",
  plot = combined_plot_2022_svnt,    
  device = "pdf",
  width = 12, 
  height = 6
)
```

#Print SVNT 2022 Data Charts
```{r}
inact_summary_2022_svnt <- inact_svnt_long_2022 %>%
  group_by(time_point, num_vaccines) %>%
  summarise(
    N = sum(!is.na(titer_value)),  # Count only non-NA values
    Mean = round(mean(titer_value, na.rm = TRUE), 1),
    SD = round(sd(titer_value, na.rm = TRUE), 1),
    Median = round(median(titer_value, na.rm = TRUE), 1),
    Q1 = round(quantile(titer_value, 0.25, na.rm = TRUE), 1),
    Q3 = round(quantile(titer_value, 0.75, na.rm = TRUE), 1),
    .groups = 'drop'
  ) %>%
  arrange(time_point, num_vaccines)

inact_summary_2022_svnt

mrna_summary_2022_svnt <- mrna_svnt_long_2022 %>%
  group_by(time_point, num_vaccines) %>%
  summarise(
    N = sum(!is.na(titer_value)),  # Count only non-NA values
    Mean = round(mean(titer_value, na.rm = TRUE), 1),
    SD = round(sd(titer_value, na.rm = TRUE), 1),
    Median = round(median(titer_value, na.rm = TRUE), 1),
    Q1 = round(quantile(titer_value, 0.25, na.rm = TRUE), 1),
    Q3 = round(quantile(titer_value, 0.75, na.rm = TRUE), 1),
    .groups = 'drop'
  ) %>%
  arrange(time_point, num_vaccines)

mrna_summary_2022_svnt
```


##############################

# Make Inactivated 2022 Secondary
```{r}
df_inact_2022_plot <- inact_svnt_long_2022 %>%
  filter(time_point %in% c("Baseline", "Step 1")) %>%
  pivot_wider(names_from = time_point, values_from = titer_value) %>%
  filter(!is.na(Baseline) & !is.na(`Step 1`)) %>%
  mutate(
    num_vaccines = factor(num_vaccines)
  )

p_linear_inact_2022 <- ggplot(df_inact_2022_plot, aes(x = Baseline, y = `Step 1`, color = num_vaccines)) +
  geom_abline(intercept = 0, slope = 1, linetype = "dotted", color = "black", size = 0.8) +
  geom_jitter(aes(shape = num_vaccines), width = 0.5, height = 0.5, size = 2.4, alpha = 0.5, stroke = 0.2) +
  geom_smooth(
    aes(group = num_vaccines, fill = num_vaccines),
    method = "lm",
    se = TRUE,
    size = 0.9,
    alpha = 0.18
  ) +
  scale_color_manual(values = vaccine_colors, name = "Baseline\nVaccine") +
  scale_fill_manual(values = vaccine_colors, name = "Baseline\nVaccine") +
  scale_shape_manual(values = c(16, 17, 15), name = "Baseline\nVaccine") +
  scale_x_continuous(
    breaks = seq(0, 100, by = 20),
    limits = c(0, 100)
  ) +
  scale_y_continuous(
    breaks = seq(0, 100, by = 20),
    limits = c(0, 100)
  ) +
  coord_cartesian(expand = FALSE) +
  labs(
    x = "Baseline sVNT (%)",
    y = "Step 1 sVNT (%)",
    title = "Inactivated (2022)"
  ) +
  theme_classic(base_size = 14) +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold", size = 16),
    legend.position = "right",
    legend.title = element_text(face = "bold", size = 11),
    legend.text = element_text(size = 10),
    axis.title = element_text(face = "bold", size = 12),
    axis.text = element_text(size = 10),
    panel.grid.major = element_line(color = "grey90", size = 0.25),
    panel.grid.minor = element_blank()
  )

print(p_linear_inact_2022)
```


# Make mRNA 2022 Secondary
```{r}
df_mrna_2022_plot <- mrna_svnt_long_2022 %>%
  filter(time_point %in% c("Baseline", "Step 1")) %>%
  pivot_wider(names_from = time_point, values_from = titer_value) %>%
  filter(!is.na(Baseline) & !is.na(`Step 1`)) %>%
  mutate(
    num_vaccines = factor(num_vaccines)
  ) %>%
  arrange(num_vaccines)

p_linear_mrna_2022 <- ggplot(df_mrna_2022_plot, aes(x = Baseline, y = `Step 1`, color = num_vaccines)) +
  geom_abline(intercept = 0, slope = 1, linetype = "dotted", color = "black", size = 0.8) +
  geom_jitter(aes(shape = num_vaccines), width = 0.5, height = 0.5, size = 2.4, alpha = 0.5, stroke = 0.2) +
  scale_color_manual(values = vaccine_colors, name = "Number of\nVaccines") +
  scale_fill_manual(values = vaccine_colors, name = "Number of\nVaccines") +
  scale_shape_manual(values = c(16, 17, 15), name = "Number of\nVaccines") +
  scale_x_continuous(
    breaks = seq(0, 100, by = 20),
    limits = c(0, 100)
  ) +
  scale_y_continuous(
    breaks = seq(90, 100, by = 2),
    limits = c(90, 100)
  ) +
  coord_cartesian(expand = FALSE) +
  labs(
    x = "Baseline sVNT (%)",
    y = "Step 1 sVNT (%)",
    title = "mRNA (2022)"
  ) +
  theme_classic(base_size = 14) +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold", size = 16),
    legend.position = "none",
    legend.title = element_text(face = "bold", size = 11),
    legend.text = element_text(size = 10),
    axis.title = element_text(face = "bold", size = 12),
    axis.text = element_text(size = 10),
    panel.grid.major = element_line(color = "grey90", size = 0.25),
    panel.grid.minor = element_blank()
  )

print(p_linear_mrna_2022)
```

# Print 2022 Plots Secondary Both
```{r}
combined_plot_2022_log_svnt <- p_linear_mrna_2022 + p_linear_inact_2022 +
  plot_annotation(
    tag_levels = "A",
    title = "Excluding Omicron"
  ) +
  plot_layout(guides = "collect") 

print(combined_plot_2022_log_svnt)

ggsave(
  filename = "combined_plot_2022_scatter_svnt.pdf",
  plot = combined_plot_2022_log_svnt,
  device = "pdf",
  width = 12,
  height = 6,
  units = "in"
)
```

# Scatter plot sample sizes 2022 
```{r}
mrna_scatter_summary_2022 <- df_mrna_2022_plot %>%
  group_by(num_vaccines) %>%
  summarise(
    N = n(),  
    Baseline_Mean = round(mean(Baseline, na.rm = TRUE), 1),
    Baseline_SD = round(sd(Baseline, na.rm = TRUE), 1),
    Baseline_Median = round(median(Baseline, na.rm = TRUE), 1),
    Baseline_Q1 = round(quantile(Baseline, 0.25, na.rm = TRUE), 1),
    Baseline_Q3 = round(quantile(Baseline, 0.75, na.rm = TRUE), 1),
    Step1_Mean = round(mean(`Step 1`, na.rm = TRUE), 1),
    Step1_SD = round(sd(`Step 1`, na.rm = TRUE), 1),
    Step1_Median = round(median(`Step 1`, na.rm = TRUE), 1),
    Step1_Q1 = round(quantile(`Step 1`, 0.25, na.rm = TRUE), 1),
    Step1_Q3 = round(quantile(`Step 1`, 0.75, na.rm = TRUE), 1),
    .groups = 'drop'
  )

print(mrna_scatter_summary_2022)

inact_scatter_summary_2022 <- df_inact_2022_plot %>%
  group_by(num_vaccines) %>%
  summarise(
    N = n(),  
    Baseline_Mean = round(mean(Baseline, na.rm = TRUE), 1),
    Baseline_SD = round(sd(Baseline, na.rm = TRUE), 1),
    Baseline_Median = round(median(Baseline, na.rm = TRUE), 1),
    Baseline_Q1 = round(quantile(Baseline, 0.25, na.rm = TRUE), 1),
    Baseline_Q3 = round(quantile(Baseline, 0.75, na.rm = TRUE), 1),
    Step1_Mean = round(mean(`Step 1`, na.rm = TRUE), 1),
    Step1_SD = round(sd(`Step 1`, na.rm = TRUE), 1),
    Step1_Median = round(median(`Step 1`, na.rm = TRUE), 1),
    Step1_Q1 = round(quantile(`Step 1`, 0.25, na.rm = TRUE), 1),
    Step1_Q3 = round(quantile(`Step 1`, 0.75, na.rm = TRUE), 1),
    .groups = 'drop'
  )

print(inact_scatter_summary_2022)
```

################################################################################

# 2021 Plots 

# mrna 2021 plot MAIN
```{r, warning = FALSE}
mrna_plot_svnt_2021 <- ggplot(mrna_svnt_long_2021, aes(x = time_point, y = titer_value, 
                                                  color = as.factor(num_vaccines), 
                                                  fill = as.factor(num_vaccines))) +
  geom_point(alpha = 0.2, position = position_jitterdodge(jitter.width = 0.15, 
                                              dodge.width = 0.8,
                                              seed = 123),
             size = 2, alpha = 0.5) +
  geom_smooth(aes(group = as.factor(num_vaccines)),
              method = "loess",
              se = TRUE,
              alpha = 0.2,
              size = 1.2) +
  # Mean points
  stat_summary(aes(group = as.factor(num_vaccines)),
               fun = mean,
               geom = "point",
               size = 4,
               position = position_dodge(width = 0.8)) +
  scale_color_manual(values = vaccine_colors, name = "Baseline \nVaccine") +
  scale_fill_manual(values = vaccine_colors, name = "Baseline \nVaccine") +
  scale_y_continuous(breaks = seq(0, 100, by = 10),
                     expand = c(0, 0)) +
  coord_cartesian(ylim = c(50, 105)) +  # Added coord_cartesian with 50-105 range
  labs(x = "Time Point", 
       y = "sVNT (%)",
       color = "Baseline \nVaccine",
       fill = "Baseline \nVaccine",
       subtitle = "Excluding Omicron",
       title = "mRNA (2021)") +
  theme_classic(base_size = 14) +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold", size = 16),
    plot.subtitle = element_text(hjust = 0.5, size = 12, color = "gray30"),
    legend.position = "right",
    legend.title = element_text(face = "bold"),
    axis.text.x = element_text(angle = 0, size = 12),
    axis.text.y = element_text(size = 12),
    axis.title = element_text(face = "bold"),
    panel.grid.major = element_line(color = "gray90", size = 0.2),
    panel.grid.minor = element_blank()
  )

mrna_plot_svnt_2021

ggsave(
  filename = "mrna_plot_svnt_2021.pdf",
  plot = mrna_plot_svnt_2021,
  device = "pdf",
  width = 12,
  height = 6,
  units = "in"
)
```


#Combined Plot for Printing 
```{r, warning = FALSE}
combined_plot_2021_elisa <- mrna_plot_elisa_2021 + inact_plot_elisa_2021 +
  plot_annotation(
    tag_levels = "A"  
  ) +
  plot_layout(guides = "collect") 

print(combined_plot_2021_elisa)

ggsave(
  filename = "combined_plot_2021_elisa.pdf",
  plot = combined_plot_2021_elisa,
  device = "pdf",
  width = 12,
  height = 6,
  units = "in"
)
```

# 2021 Summary Statistics SVNT
```{r}
mrna_summary_2021_svnt <- mrna_svnt_long_2021 %>%
  group_by(time_point, num_vaccines) %>%
  summarise(
    N = sum(!is.na(titer_value)),  # Count only non-NA values
    Mean = round(mean(titer_value, na.rm = TRUE), 1),
    SD = round(sd(titer_value, na.rm = TRUE), 1),
    Median = round(median(titer_value, na.rm = TRUE), 1),
    Q1 = round(quantile(titer_value, 0.25, na.rm = TRUE), 1),
    Q3 = round(quantile(titer_value, 0.75, na.rm = TRUE), 1),
    .groups = 'drop'
  ) %>%
  arrange(time_point, num_vaccines)

mrna_summary_2021_svnt

inact_summary_2021_svnt <- inact_svnt_long_2021 %>%
  group_by(time_point, num_vaccines) %>%
  summarise(
    N = sum(!is.na(titer_value)),  # Count only non-NA values
    Mean = round(mean(titer_value, na.rm = TRUE), 1),
    SD = round(sd(titer_value, na.rm = TRUE), 1),
    Median = round(median(titer_value, na.rm = TRUE), 1),
    Q1 = round(quantile(titer_value, 0.25, na.rm = TRUE), 1),
    Q3 = round(quantile(titer_value, 0.75, na.rm = TRUE), 1),
    .groups = 'drop'
  ) %>%
  arrange(time_point, num_vaccines)

inact_summary_2021_svnt
```

# Make mRNA 2021 Secondary
```{r}
df_mrna_2021_plot <- mrna_svnt_long_2021 %>%
  filter(time_point %in% c("Baseline", "Step 1")) %>%
  pivot_wider(names_from = time_point, values_from = titer_value) %>%
  filter(!is.na(Baseline) & !is.na(`Step 1`)) %>%
  mutate(
    num_vaccines = factor(num_vaccines)
  )

p_linear_mrna_2021 <- ggplot(df_mrna_2021_plot, aes(x = Baseline, y = `Step 1`, color = num_vaccines)) +
  geom_abline(intercept = 0, slope = 1, linetype = "dotted", color = "black", size = 0.8) +
  geom_jitter(aes(shape = num_vaccines), width = 0.5, height = 0.5, size = 2.4, alpha = 0.5, stroke = 0.2) +
  scale_color_manual(values = vaccine_colors, name = "Baseline\nVaccine") +
  scale_fill_manual(values = vaccine_colors, name = "Baseline\nVaccine") +
  scale_shape_manual(values = c(16, 17, 15), name = "Baseline\nVaccine") +
  geom_smooth(
    aes(group = num_vaccines, fill = num_vaccines),
    method = "lm",
    se = TRUE,
    size = 0.9,
    alpha = 0.18
  ) +
  scale_x_continuous(
    breaks = seq(0, 100, by = 20),
    limits = c(0, 100)
  ) +
  scale_y_continuous(
    breaks = seq(40, 100, by = 10),
    limits = c(40, 100)
  ) +
  coord_cartesian(expand = FALSE) +
  labs(
    x = "Baseline sVNT (%)",
    y = "Step 1 sVNT (%)",
    title = "mRNA (2021)",
    subtitle = "Excluding Omicron"
  ) +
  theme_classic(base_size = 14) +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold", size = 16),
    plot.subtitle = element_text(hjust = 0.5, size = 12, color = "gray30"),
    legend.position = "right",
    legend.title = element_text(face = "bold", size = 11),
    legend.text = element_text(size = 10),
    axis.title = element_text(face = "bold", size = 12),
    axis.text = element_text(size = 10),
    panel.grid.major = element_line(color = "grey90", size = 0.25),
    panel.grid.minor = element_blank()
  )

print(p_linear_mrna_2021)

ggsave(
  filename = "p_linear_mrna_2021.pdf",
  plot = p_linear_mrna_2021,
  device = "pdf",
  width = 12,
  height = 6,
  units = "in"
)
```

#mRNA 2021 Sample Sizes Secondary 
```{r}
mrna_scatter_n_2021 <- df_mrna_2021_plot %>%
  group_by(num_vaccines) %>%
  summarise(N = n())

print(mrna_scatter_n_2021)
```


################################################################################

# ELISA VALUE GRAPHS 

```{r}
df_mrna_elisa_2021_plot <- mrna_elisa_long_2021 %>%
  filter(time_point %in% c("Baseline", "Step 1")) %>%
  pivot_wider(names_from = time_point, values_from = titer_value) %>%
  filter(!is.na(Baseline) & !is.na(`Step 1`)) %>%
  mutate(
    Baseline_eps = Baseline + eps,
    Step1_eps   = `Step 1` + eps,
    num_vaccines = factor(num_vaccines)
  )

p_elisa_mrna_2021 <- ggplot(df_mrna_elisa_2021_plot, aes(x = Baseline_eps, y = Step1_eps, color = num_vaccines)) +
  geom_abline(intercept = 0, slope = 1, linetype = "dotted", color = "black", size = 0.8) +
  geom_jitter(aes(shape = num_vaccines), width = 0.02, height = 0.02, size = 2.4, alpha = 0.6, stroke = 0.2) +
  geom_smooth(aes(group = num_vaccines, fill = num_vaccines),
              method = "lm", se = TRUE, size = 0.9, alpha = 0.18) +
  scale_color_manual(values = vaccine_colors, name = "Number of\nVaccines") +
  scale_fill_manual(values = vaccine_colors, name = "Number of\nVaccines") +
  scale_shape_manual(values = c(16, 17, 15), name = "Number of\nVaccines") +
  scale_x_continuous(limits = c(0, 6.5), breaks = seq(0, 6, by = 1), expand = c(0,0)) +
  scale_y_continuous(limits = c(0, 6.5), breaks = seq(0, 6, by = 1), expand = c(0,0)) +
  coord_cartesian(expand = FALSE) +
  labs(
    x = "Baseline ELISA",
    y = "Step 1 ELISA",
    title = "mRNA (2021) — ELISA"
  ) +
  theme_classic(base_size = 14) +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold", size = 16),
    legend.position = "right",
    legend.title = element_text(face = "bold", size = 11),
    legend.text = element_text(size = 10),
    axis.title = element_text(face = "bold", size = 12),
    axis.text = element_text(size = 10),
    panel.grid.major = element_line(color = "grey90", size = 0.25),
    panel.grid.minor = element_blank()
  )

print(p_elisa_mrna_2021)

ggsave(
  filename = "p_elisa_mrna_2021.pdf",
  plot = p_elisa_mrna_2021,    
  device = "pdf",
  width = 12, 
  height = 6
)
```

# mrna 2021 Plot MAIN elisa
```{r, warning= FALSE}
mrna_plot_elisa_2021 <- ggplot(mrna_elisa_long_2021 %>% filter(time_point %in% c("Baseline", "Step 1")), aes(x = time_point, y = titer_value, 
                                                  color = as.factor(num_vaccines), 
                                                  fill = as.factor(num_vaccines))) +
  geom_point(alpha = 0.2, position = position_jitterdodge(jitter.width = 0.15, 
                                              dodge.width = 0.8,
                                              seed = 123),
             size = 2, alpha = 0.5) +
  geom_smooth(aes(group = as.factor(num_vaccines)),
              method = "lm",
              se = TRUE,
              alpha = 0.2,
              size = 1.2) +
  # Mean points
  stat_summary(aes(group = as.factor(num_vaccines)),
               fun = mean,
               geom = "point",
               size = 4,
               position = position_dodge(width = 0.8)) +
  scale_color_manual(values = vaccine_colors, name = "Number of\nVaccines") +
  scale_fill_manual(values = vaccine_colors, name = "Number of\nVaccines") +
  scale_y_continuous(breaks = seq(0, 6, by = 0.6),
                     expand = c(0, 0)) +
  coord_cartesian(ylim = c(0, 6.5)) +  # Added coord_cartesian with 50-105 range
  labs(x = "Time Point", 
       y = "ELISA",
       color = "Number of\nVaccines",
       fill = "Number of\nVaccines",
       title = "mRNA (2021)") +
  theme_classic(base_size = 14) +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold", size = 16),
    plot.subtitle = element_text(hjust = 0.5, size = 12, color = "gray30"),
    legend.position = "right",
    legend.title = element_text(face = "bold"),
    axis.text.x = element_text(angle = 0, size = 12),
    axis.text.y = element_text(size = 12),
    axis.title = element_text(face = "bold"),
    panel.grid.major = element_line(color = "gray90", size = 0.2),
    panel.grid.minor = element_blank()
  )

mrna_plot_elisa_2021
```

# Inactivated 2021 Plot MAIN elisa
```{r, warning = FALSE}
inact_plot_elisa_2021 <- ggplot(inact_elisa_long_2021 %>% filter(time_point %in% c("Baseline", "Step 1")), aes(x = time_point, y = titer_value, 
                                                  color = as.factor(num_vaccines), 
                                                  fill = as.factor(num_vaccines))) +
  geom_point(alpha = 0.2, position = position_jitterdodge(jitter.width = 0.15, 
                                              dodge.width = 0.8,
                                              seed = 123),
             size = 2, alpha = 0.5) +
  geom_smooth(aes(group = as.factor(num_vaccines)),
              method = "lm",
              se = TRUE,
              alpha = 0.2,
              size = 1.2) +
  stat_summary(aes(group = as.factor(num_vaccines)),
               fun = mean,
               geom = "point",
               size = 4,
               position = position_dodge(width = 0.8)) +
  scale_color_manual(values = vaccine_colors, name = "Number of\nVaccines") +
  scale_fill_manual(values = vaccine_colors, name = "Number of\nVaccines") +
  scale_y_continuous(breaks = seq(0, 6, by = 0.5),
                     expand = c(0, 0)) +
  coord_cartesian(ylim = c(0, 6.5)) +  
  labs(x = "Time Point", 
       y = "ELISA",
       color = "Number of\nVaccines",
       fill = "Number of\nVaccines",
       title = "Inactivated (2021)") +
  theme_classic(base_size = 14) +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold", size = 16),
    plot.subtitle = element_text(hjust = 0.5, size = 12, color = "gray30"),
    legend.position = "right",
    legend.title = element_text(face = "bold"),
    axis.text.x = element_text(angle = 0, size = 12),
    axis.text.y = element_text(size = 12),
    axis.title = element_text(face = "bold"),
    panel.grid.major = element_line(color = "gray90", size = 0.2),
    panel.grid.minor = element_blank()
  )

inact_plot_elisa_2021
```
################################################################################


```{r}
mrna_brands <- c(1, 3, 9, 10, 11, 12, 13)

mrna_omicron_data <- data %>%
  filter(
    dose4_brand %in% mrna_brands &
    (is.na(dose5_brand) | dose5_brand %in% mrna_brands) &
    (is.na(dose6_brand) | dose6_brand %in% mrna_brands)
  )

mrna_omicron_sample_sizes <- data.frame(
  Visit = c("v4", "v5", "v6"),
  N = c(
    sum(!is.na(mrna_omicron_data$v4_svnt_ba5)),
    sum(!is.na(mrna_omicron_data$v5_svnt_ba5)),
    sum(!is.na(mrna_omicron_data$v6_svnt_ba5))
  )
)

print(mrna_omicron_sample_sizes)
```
