---
title: "analysis"
author: "Tanmayi Patharkar"
date: "`r Sys.Date()`"
output: html_document
---
#load packages 
```{r}
library(librarian)
shelf(dplyr) 
shelf(tidyverse)
shelf(readxl)
shelf(tidyr)
shelf(rlang)
shelf(patchwork)
```

#data loading and processig 
```{r}
data <- read.csv("./data/data_03102025.csv") 
dict <- read_excel("./data/dict.xlsx")

data <- data %>%
  mutate(posrat_p1_date = as.Date(posrat_p1_date, format = "%Y-%m-%d")) %>%
  mutate(across(contains("date"), \(x) as.Date(x, format = "%Y-%m-%d"))) 
```

#Preliminary Count Analysis 
```{r}
dose_count <- data %>%
  summarise(across(matches("^dose[1-8]_date$"), ~ sum(!is.na(.), na.rm = TRUE), .names = "count_{col}")) %>%
  pivot_longer(everything(), names_to = "dose", values_to = "count")

ggplot(dose_count, aes(x = dose, y = count)) +
  geom_col(fill = "skyblue") +
  geom_text(aes(label = count), vjust = -0.5, size = 3) +
  scale_y_continuous(
    limits = c(0, 2000),
    breaks = seq(0, 2000, by = 250),
    minor_breaks = seq(0, 2000, by = 50),
    expand = c(0, 0.02)
  ) +
  labs(title = "Number of Participants by Dose", x = "Dose", y = "Count") +
  theme_minimal() +
  theme(
    panel.grid.major.y = element_line(color = "gray80"),
    panel.grid.minor.y = element_line(color = "gray92"),
    axis.text.x = element_text(angle = 45, hjust = 1)
  )
```

#Load Vaccine Dosages 
```{r}
data <- data %>%
  mutate(
    one_dose_permutation = paste(dose1_brand),
    two_dose_permutation = paste(dose1_brand, dose2_brand, sep = "-"),
    three_dose_permutation = paste(dose1_brand, dose2_brand, dose3_brand, sep = "-"),
    four_dose_permutation = paste(dose1_brand, dose2_brand, dose3_brand, dose4_brand, sep = "-"),
    five_dose_permutation = paste(dose1_brand, dose2_brand, dose3_brand, dose4_brand, dose5_brand, sep = "-")
  )

#Make separate data frames for each vaccine permutation
one_dose_data <- data %>%
  filter(!grepl("NA", one_dose_permutation))

two_dose_data <- data %>%
  filter(!grepl("NA", two_dose_permutation))

three_dose_data <- data %>%
  filter(!grepl("NA", three_dose_permutation))

four_dose_data <- data %>%
  filter(!grepl("NA", four_dose_permutation))

five_dose_data <- data %>%
  filter(!grepl("NA", five_dose_permutation))
```

#Permutation Counts
```{r}
one_permutation_count <- one_dose_data %>%
  group_by(one_dose_permutation) %>% 
  summarise(count = n(), .groups = 'drop')

two_permutation_count <- two_dose_data %>%
  group_by(two_dose_permutation) %>% 
  summarise(count = n(), .groups = 'drop')

three_permutation_count <- three_dose_data %>%
  group_by(three_dose_permutation) %>% 
  summarise(count = n(), .groups = 'drop')

four_permutation_count <- four_dose_data %>%
  group_by(four_dose_permutation) %>% 
  summarise(count = n(), .groups = 'drop')

five_permutation_count <- five_dose_data %>%
  group_by(five_dose_permutation) %>% 
  summarise(count = n(), .groups = 'drop')
```

#Antibody Value Measurements
```{r}
source("scripts/fc_vaccine_perm.R")
```

#Baseline Value Measurements
```{r}
source("scripts/fc_get_baselines.R")
```


#Baseline Value Assessment 
```{r}
baseline_elisa <- get_baselines(data, "elisa_wt")  
baseline_svnt <- get_baselines(data, "svnt_wt")    

print(head(baseline_elisa))
print(head(baseline_svnt))
```
#Find Common Individuals 

Find Individuals that have data for BASELINE + AND ALL DOSES 
```{r}
three_dose_data$base_elisa <- baseline_elisa$baseline_value[match(three_dose_data$id, baseline_elisa$id)] 

three_dose_elisa_homologous <- three_dose_data %>%
  filter(!is.na(base_elisa) & !is.na(v1_elisa_wt) & !is.na(v2_elisa_wt) & !is.na(v3_elisa_wt)) %>%
  filter(grepl("1-1-1|4-4-4", three_dose_permutation))

three_dose_elisa_homologous
```

```{r}
median_elisa <- baseline_elisa %>%
  group_by(dose1_brand) %>%
  summarise(median_value = median(baseline_value, na.rm = TRUE), .groups = 'drop')

median_svnt <- baseline_svnt %>%
  group_by(dose1_brand) %>%
  summarise(median_value = median(baseline_value, na.rm = TRUE), .groups = 'drop')


baseline_elisa$elisa_wt <- as.numeric(baseline_elisa$baseline_value)
baseline_svnt$svnt_wt <- as.numeric(baseline_svnt$baseline_value)
```


```{r}
one_labels <- c("1" = " B", "4" = "S")

elisa_baseline_wt <- ggplot() +
  geom_jitter(data = baseline_elisa,
              aes(x = factor(dose1_brand), y = baseline_value, color = factor(dose1_brand)),
              alpha = 0.8, width = 0.18, size = 2.5) +
  geom_crossbar(data = median_elisa,
                 aes(x = factor(dose1_brand), y = median_value, 
                     ymin = median_value, ymax = median_value),  
                 width = 0.5, colour = "black", size = 0.5) +
  scale_x_discrete(labels = one_labels, expand = expansion(add = c(0.5, 0.5))) +
  scale_y_continuous(limits = c(0, 6), breaks = seq(0, 6, by = 0.5)) +
  scale_color_manual(values = c("1" = "#1F77B4", "4" = "#FF7F0E")) +
  labs(x = NULL,
       y = "WT RBD ELISA (OD value)",
       caption = "Baseline") +  
  theme_bw(base_size = 12) +  
    theme(plot.caption = element_text(face = "bold", size = 10, hjust = 0.5),
        plot.title = element_text(face = "bold", size = 14),
        axis.title = element_text(face = "bold"),
        axis.text.x = element_text(angle = 0, hjust = 0.5, vjust = 0.5, face = "bold"),  
        panel.grid.major = element_blank(),  
        panel.grid.minor = element_blank(),  
        axis.ticks = element_line(),  
        legend.position = "none",
        panel.border = element_blank(),
        axis.line = element_line(size = 0.5, color = "black", linetype = "solid")
  )

elisa_baseline_wt
```


```{r}
one_labels <- c("1" = " B", "4" = "S")

svnt_baseline_wt <- ggplot() +
  geom_jitter(data = baseline_svnt,
              aes(x = factor(dose1_brand), y = baseline_value, color = factor(dose1_brand)),
              alpha = 0.8, width = 0.18, size = 2.5) +
  geom_crossbar(data = median_elisa,
                 aes(x = factor(dose1_brand), y = median_value, 
                     ymin = median_value, ymax = median_value),  
                 width = 0.5, colour = "black", size = 0.5) +
  scale_x_discrete(labels = one_labels, expand = expansion(add = c(0.5, 0.5))) +
  scale_y_continuous(limits = c(0, 110), breaks = seq(0, 100, by = 20)) +
  scale_color_manual(values = c("1" = "#1F77B4", "4" = "#FF7F0E")) + 
  labs(x = NULL,
       y = "WT sVNT Inhibition (%)",
       caption = "Baseline") +  
  theme_bw(base_size = 12) +  
  theme(plot.caption = element_text(face = "bold", size = 10, hjust = 0.5),
        plot.title = element_text(face = "bold", size = 14),
        axis.title = element_text(face = "bold"),
        axis.text.x = element_text(angle = 0, hjust = 0.5, vjust = 0.5, face = "bold"),  
        panel.grid.major = element_blank(),  
        panel.grid.minor = element_blank(),  
        axis.ticks = element_line(),  
        legend.position = "none",
        panel.border = element_blank(),
        axis.line = element_line(size = 0.5, color = "black", linetype = "solid")
  )

svnt_baseline_wt
```

#POST INFECTION 

#calculate FIRST infection recorded 
```{r}
calculate_earliest_date <- function(data) {
  data <- data %>%
    mutate(earliest_posdate = pmin(posdate_p1, posdate_p2, posdate_p3, posdate_p4, na.rm = TRUE)) %>%
    filter(!is.na(earliest_posdate))  # Remove rows with NA earliest_posdate
  return(data)
}

first_infection_data <- calculate_earliest_date(data)
```

```{r}
extract_valid_dates_with_weights <- function(data) {
  if (!"earliest_posdate" %in% colnames(data)) {
    data <- calculate_earliest_date(data)
  }

  date_cols <- paste0("r", 1:11, "_date")
  data[date_cols] <- lapply(data[date_cols], as.Date)

  elisa_weight_cols <- paste0("r", 1:11, "_elisa_wt")
  svnt_weight_cols <- paste0("r", 1:11, "_svnt_wt")

  long_data <- data %>%
    pivot_longer(
      cols = all_of(date_cols),
      names_to = "r_index",
      values_to = "valid_date"
    ) %>%
    rowwise() %>%
    mutate(
      rX_elisa_wt = case_when(
        r_index == "r1_date" ~ r1_elisa_wt,
        r_index == "r2_date" ~ r2_elisa_wt,
        r_index == "r3_date" ~ r3_elisa_wt,
        r_index == "r4_date" ~ r4_elisa_wt,
        r_index == "r5_date" ~ r5_elisa_wt,
        r_index == "r6_date" ~ r6_elisa_wt,
        r_index == "r7_date" ~ r7_elisa_wt,
        r_index == "r8_date" ~ r8_elisa_wt,
        r_index == "r9_date" ~ r9_elisa_wt,
        r_index == "r10_date" ~ r10_elisa_wt,
        r_index == "r11_date" ~ r11_elisa_wt,
        TRUE ~ NA_real_
      ),
      rX_svnt_wt = case_when(
        r_index == "r1_date" ~ r1_svnt_wt,
        r_index == "r2_date" ~ r2_svnt_wt,
        r_index == "r3_date" ~ r3_svnt_wt,
        r_index == "r4_date" ~ r4_svnt_wt,
        r_index == "r5_date" ~ r5_svnt_wt,
        r_index == "r6_date" ~ r6_svnt_wt,
        r_index == "r7_date" ~ r7_svnt_wt,
        r_index == "r8_date" ~ r8_svnt_wt,
        r_index == "r9_date" ~ r9_svnt_wt,
        r_index == "r10_date" ~ r10_svnt_wt,
        r_index == "r11_date" ~ r11_svnt_wt,
        TRUE ~ NA_real_
      )
    ) %>%
    filter(
      !is.na(valid_date) & valid_date > (earliest_posdate + 30) & valid_date <= (earliest_posdate + 60)
    )

  return(long_data %>% select(valid_date, rX_elisa_wt, rX_svnt_wt))
}

data_with_earliest <- calculate_earliest_date(data)

valid_dates_result <- extract_valid_dates_with_weights(data_with_earliest)

print(head(valid_dates_result))
```

```{r}
median_svnt <- median(valid_dates_result$rX_svnt_wt, na.rm = TRUE) 
median_df_svnt <- data.frame(x = factor(1), median = median_svnt)

post_infection_svnt <- ggplot(valid_dates_result, aes(x = factor(1), y = rX_svnt_wt)) + 
  geom_jitter(width = 0.2, alpha = 0.8, size = 2.5, colour = "darkred") + 
  geom_crossbar( data = median_df_svnt, aes(x = x, y = median, ymin = median, ymax = median), width = 0.5, colour = "black", size = 0.5) +
  scale_x_discrete(labels = c(""), expand = expansion(add = c(0.5, 0.5))) + 
  scale_y_continuous(limits = c(0, 110), breaks = seq(0, 100, by = 20)) + labs(x = NULL, y = "WT sVNT Inhibition (%)", caption = "Cohort Post-Infection") + 
  theme_bw(base_size = 12) + 
  theme( plot.caption = element_text(face = "bold", size = 10, hjust = 0.5), 
         plot.title = element_text(face = "bold", size = 14), axis.title = element_text(face = "bold"), axis.text.x = element_text(face = "bold"), 
         panel.grid.major = element_blank(), panel.grid.minor = element_blank(), 
         axis.ticks = element_blank(), legend.position = "none", 
         panel.border = element_blank(), 
         axis.line = element_line(size = 0.5, color = "black") )

post_infection_svnt
```

```{r}
median_elisa<- median(valid_dates_result$rX_elisa_wt, na.rm = TRUE) 
median_df_elisa <- data.frame(x = factor(1), median = median_elisa)

post_infection_elisa <- ggplot(valid_dates_result, aes(x = factor(1), y = rX_elisa_wt)) + 
  geom_jitter(width = 0.2, alpha = 0.8, size = 2.5, colour = "darkred") + 
  geom_crossbar(data = median_df_elisa, aes(x = x, y = median, ymin = median, ymax = median), width = 0.5, colour = "black", size = 0.5) +
  scale_x_discrete(labels = c(""), expand = expansion(add = c(0.5, 0.5))) + 
  scale_y_continuous(limits = c(0, 6), breaks = seq(0, 6, by = 0.5)) + labs(x = NULL, y = "WT RBD ELISA (OD value)", caption = "Cohort Post-Infection") + 
  theme_bw(base_size = 12) + 
  theme( plot.caption = element_text(face = "bold", size = 10, hjust = 0.5), 
         plot.title = element_text(face = "bold", size = 14), axis.title = element_text(face = "bold"), axis.text.x = element_text(face = "bold"), 
         panel.grid.major = element_blank(), panel.grid.minor = element_blank(), 
         axis.ticks = element_blank(), legend.position = "none", 
         panel.border = element_blank(), 
         axis.line = element_line(size = 0.5, color = "black") )

post_infection_elisa

ggsave("post_infection_elisa.pdf", plot = post_infection_elisa, width = 10 , height = 6)
```



##SVNT_WT

##ONE
```{r}
one_svnt_wt <- fc_perm_summary(one_dose_data, one_dose_permutation, v1_svnt_wt, min_n = 5, dose_label = "1 Dose")

one_valid_perms      <- one_svnt_wt$valid_perms
one_dose_medians     <- one_svnt_wt$medians
one_n_levels         <- one_svnt_wt$n_levels
one_mid_x            <- one_svnt_wt$mid_x

print(one_svnt_wt$valid_perm_count)
```

```{r}
one_labels <- c("1" = " B", "4" = " S")

response_colq <- "v1_svnt_wt"

one_svnt_wt_plot <- ggplot() +
  geom_jitter(data = one_valid_perms,
              aes_string(x = "one_dose_permutation", y = response_colq, color = "one_dose_permutation"),
              alpha = 0.8, width = 0.18, size = 2.5) +
  geom_crossbar(data = one_dose_medians,
                aes_string(x = "one_dose_permutation", y = "median",  
                           ymin = "median", ymax = "median"),  
                width = 0.5, colour = "black", size = 0.5) +  
  scale_x_discrete(labels = one_labels, expand = expansion(add = c(0.5, 0.5))) +
  scale_y_continuous(limits = c(0, 110), breaks = seq(0, 100, by = 20)) +
  scale_color_manual(values = c("1" = "#1F77B4", "4" = "#FF7F0E")) + 
  labs(x = NULL,
       y = "WT sVNT Inhibition (%)",
       caption = "1 Dose") +  
  theme_bw(base_size = 12) +  
    theme(plot.caption = element_text(face = "bold", size = 10, hjust = 0.5),
        plot.title = element_text(face = "bold", size = 14),
        axis.title = element_text(face = "bold"),
        axis.text.x = element_text(angle = 0, hjust = 0.5, vjust = 0.5, face = "bold"),  
        panel.grid.major = element_blank(),  
        panel.grid.minor = element_blank(),  
        axis.ticks = element_line(),  
        legend.position = "none",
        panel.border = element_blank(),
        axis.line = element_line(size = 0.5, color = "black", linetype = "solid")
  )

one_svnt_wt_plot
```


##TWO 
```{r}
two_svnt_wt <- fc_perm_summary(two_dose_data, two_dose_permutation, v2_svnt_wt, min_n = 5, dose_label = "2 Dose")

two_valid_perms      <- two_svnt_wt$valid_perms
two_dose_medians     <- two_svnt_wt$medians
two_n_levels         <- two_svnt_wt$n_levels
two_mid_x            <- two_svnt_wt$mid_x

print(two_svnt_wt$valid_perm_count)
```

```{r}
two_labels <- c("1-1" =" B-B", "4-4" ="S-S")

response_colq <- "v2_svnt_wt"

two_svnt_wt_plot <- ggplot() +
  geom_jitter(data = two_valid_perms,
              aes(x = two_dose_permutation, y = !!sym(response_colq), color = two_dose_permutation),
              alpha = 0.8, width = 0.18, size = 2.5) +
  geom_crossbar(data = two_dose_medians,
                aes(x = two_dose_permutation, y = median, 
                    ymin = median, ymax = median),  
                width = 0.5, colour = "black", size = 0.5) +
  scale_x_discrete(labels = two_labels, limits = c("1-1", "4-4"), expand = expansion(add = c(0.5, 0.5))) +
  scale_y_continuous(limits = c(0, 110), breaks = seq(0, 100, by = 20)) +
  labs(x = NULL,
       y = "WT sVNT Inhibition (%)",
       caption = "2 Doses") +  
  theme_bw(base_size = 12) +  
  scale_color_manual(values = c("1-1" = "#1F77B4", "4-4" = "#FF7F0E")) +
    theme(plot.caption = element_text(face = "bold", size = 10, hjust = 0.5),
        plot.title = element_text(face = "bold", size = 14),
        axis.title = element_text(face = "bold"),
        axis.text.x = element_text(angle = 0, hjust = 0.5, vjust = 0.5, face = "bold"),  
        panel.grid.major = element_blank(),  
        panel.grid.minor = element_blank(),  
        axis.ticks = element_line(),  
        legend.position = "none",
        panel.border = element_blank(),
        axis.line = element_line(size = 0.5, color = "black", linetype = "solid")
  )

two_svnt_wt_plot
```


##THREE
```{r}
three_svnt_wt <- fc_perm_summary(three_dose_data, three_dose_permutation, v3_svnt_wt, min_n = 5, dose_label = "3 Dose")

three_valid_perms      <- three_svnt_wt$valid_perms
three_dose_medians     <- three_svnt_wt$medians
three_n_levels         <- three_svnt_wt$n_levels
three_mid_x            <- three_svnt_wt$mid_x

print(three_svnt_wt$valid_perm_count)
```

```{r}
three_labels <- c("4-4-1" ="S-S-B", "4-4-4" ="S-S-S", "1-1-1" = "B-B-B", "1-1-4" = "B-B-S")

response_colq <- "v3_svnt_wt"

three_svnt_wt_plot <- ggplot() +
  geom_jitter(data = three_valid_perms,
              aes(x = three_dose_permutation, y = !!sym(response_colq), color = three_dose_permutation),
              alpha = 0.8, width = 0.18, size = 2.5) +
  geom_crossbar(data = three_dose_medians,
                aes(x = three_dose_permutation, y = median, 
                    ymin = median, ymax = median),  
                width = 0.5, colour = "black", size = 0.5) +
  scale_x_discrete(labels = three_labels,limits = c("1-1-1", "4-4-4", "1-1-4", "4-4-1"), expand = expansion(add = c(0.5, 0.5))) +
  scale_y_continuous(limits = c(0, 110), breaks = seq(0, 100, by = 20)) +
  labs(x = NULL,
       y = "WT sVNT Inhibition (%)",
       caption = "3 Doses") +  
  scale_color_manual(values = c("1-1-1" = "#1F77B4", "4-4-4" = "#FF7F0E","4-4-1"= "#1B5E20", "1-1-4" = "#4A148C")) +
  theme_bw(base_size = 12) +  
    theme(plot.caption = element_text(face = "bold", size = 10, hjust = 0.5),
        plot.title = element_text(face = "bold", size = 14),
        axis.title = element_text(face = "bold"),
        axis.text.x = element_text(angle = 0, hjust = 0.5, vjust = 0.5, face = "bold"),  
        panel.grid.major = element_blank(),  
        panel.grid.minor = element_blank(),  
        axis.ticks = element_line(),  
        legend.position = "none",
        panel.border = element_blank(),
        axis.line = element_line(size = 0.5, color = "black", linetype = "solid")
  )

three_svnt_wt_plot
```

##FOUR
```{r}
four_svnt_wt <- fc_perm_summary(four_dose_data, four_dose_permutation, v4_svnt_wt, min_n = 5, dose_label = "4 Doses")

four_valid_perms      <- four_svnt_wt$valid_perms
four_dose_medians     <- four_svnt_wt$medians
four_n_levels         <- four_svnt_wt$n_levels
four_mid_x            <- four_svnt_wt$mid_x

print(four_svnt_wt$valid_perm_count)
```


```{r}
four_labels <- c("1-1-1-1" =" B-B-B-B", "4-4-1-1" =" S-S-B-B", "4-4-4-4" ="S-S-S-S","4-4-4-1" ="S-S-S-B")

response_colq <- "v4_svnt_wt"

four_svnt_wt_plot <- ggplot() +
  geom_jitter(data = four_valid_perms,
              aes(x = four_dose_permutation, y = !!sym(response_colq), color = four_dose_permutation),
              alpha = 0.8, width = 0.18, size = 2.5) +
  geom_crossbar(data = four_dose_medians,
                aes(x = four_dose_permutation, y = median, 
                    ymin = median, ymax = median),  
                width = 0.5, colour = "black", size = 0.5) +
  scale_x_discrete(labels = four_labels, limits = c("1-1-1-1", "4-4-4-4", "4-4-4-1", "4-4-1-1"), expand = expansion(add = c(0.5, 0.5))) +
  scale_y_continuous(limits = c(0, 110), breaks = seq(0, 100, by = 20)) +
  labs(x = NULL,
       y = "WT sVNT Inhibition (%)",
       caption = "4 Doses") + 
  scale_color_manual(values = c(
    "1-1-1-1" = "#1F77B4",  
    "1-1-1-9" = "#2CA02C",  
    "4-4-1-1" = "#D62728",   
    "4-4-1-9" = "#9467BD",   
    "4-4-4-4" = "#8C564B",   
    "4-4-4-1" = "#E377C2"   
  )) +
  theme_bw(base_size = 12) +  
  theme(plot.caption = element_text(face = "bold", size = 10, hjust = 0.5),
        plot.title = element_text(face = "bold", size = 14),
        axis.title = element_text(face = "bold"),
        axis.text.x = element_text(angle = 0, hjust = 0.5, vjust = 0.5, face = "bold"),  
        panel.grid.major = element_blank(),  
        panel.grid.minor = element_blank(),  
        axis.ticks = element_line(),  
        legend.position = "none",
        panel.border = element_blank(),
        axis.line = element_line(size = 0.5, color = "black", linetype = "solid")
  )

four_svnt_wt_plot
```


###PANEL ORGANIZATION

```{r}
y_limits <- c(0, 105)

svnt_baseline_wt <- svnt_baseline_wt + scale_y_continuous(limits = y_limits, breaks = seq(0, 100, by = 20)) +
  labs(y = "WT sVNT Inhibition (%)") + 
  theme(axis.text.y = element_text(size = 10), 
        axis.ticks.y = element_line(),          
        axis.line.y = element_line())   

post_infection_svnt <- post_infection_svnt + 
scale_y_continuous(limits = y_limits, breaks = seq(0, 100, by = 20)) +
  labs(y = NULL) +  
  theme(axis.text.y = element_blank(),  
        axis.ticks.y = element_blank(),  
        axis.line.y = element_blank())

one_svnt_wt_plot <- one_svnt_wt_plot + 
scale_y_continuous(limits = y_limits, breaks = seq(0, 100, by = 20)) +
  labs(y = NULL) +  
  theme(axis.text.y = element_blank(),  
        axis.ticks.y = element_blank(),  
        axis.line.y = element_blank())          

two_svnt_wt_plot <- two_svnt_wt_plot + 
  scale_y_continuous(limits = y_limits, breaks = seq(0, 100, by = 20)) +
  labs(y = NULL) +  
  theme(axis.text.y = element_blank(),  
        axis.ticks.y = element_blank(),  
        axis.line.y = element_blank())   

three_svnt_wt_plot <- three_svnt_wt_plot + 
  scale_y_continuous(limits = y_limits, breaks = seq(0, 100, by = 20)) +
  labs(y = NULL) + 
  theme(axis.text.y = element_blank(), 
        axis.ticks.y = element_blank(), 
        axis.line.y = element_blank())

four_svnt_wt_plot <- four_svnt_wt_plot + 
  scale_y_continuous(limits = y_limits, breaks = seq(0, 100, by = 20)) +
  labs(y = NULL) + 
  theme(axis.text.y = element_blank(), 
        axis.ticks.y = element_blank(), 
        axis.line.y = element_blank())

svnt_wt_combined_plot <- (svnt_baseline_wt + post_infection_svnt + one_svnt_wt_plot + 
                  two_svnt_wt_plot + 
                  three_svnt_wt_plot + 
                  four_svnt_wt_plot) + 
  plot_layout(widths = c(1.0, 1.0, 1.0, 1.0, 2.0, 2.0), ncol = 6) + plot_annotation(title = "WT sVNT", 
                  theme = theme(plot.title = element_text(face = "bold", size = 16, hjust = 0.5))) +
  theme(plot.background = element_blank(),
        plot.title = element_text(face = "bold", size = 16, hjust = 0.5),
        panel.border = element_blank(), 
        plot.margin = margin(0, 0, 0, 0))

print(svnt_wt_combined_plot)

ggsave("svnt_wt_combined_plot.pdf", plot = svnt_wt_combined_plot, width = 20 , height = 6)
```



#ELISA VALUES 

##ONE
```{r}
one_elisa_wt <- fc_perm_summary(one_dose_data, one_dose_permutation, v1_elisa_wt, min_n = 5, dose_label = "1 Dose")

one_valid_perms_e      <- one_elisa_wt$valid_perms
one_dose_medians_e     <- one_elisa_wt$medians
one_n_levels_e         <- one_elisa_wt$n_levels
one_mid_x_e            <- one_elisa_wt$mid_x

print(one_elisa_wt$valid_perm_count)
```

```{r}
one_labels <- c("1" = " B", "4" = " S")

response_colq <- "v1_elisa_wt"

one_elisa_wt_plot <- ggplot() +
  geom_jitter(data = one_valid_perms_e,
              aes_string(x = "one_dose_permutation", y = response_colq, color = "one_dose_permutation"),
              alpha = 0.8, width = 0.18, size = 2.5) +
  geom_crossbar(data = one_dose_medians_e,
                aes_string(x = "one_dose_permutation", y = "median",  
                           ymin = "median", ymax = "median"),  
                width = 0.5, colour = "black", size = 0.5) +  
  scale_x_discrete(labels = one_labels, expand = expansion(add = c(0.5, 0.5))) +
  scale_y_continuous(limits = c(0, 6), breaks = seq(0, 6, by = 0.5)) +
  scale_color_manual(values = c("1" = "#1F77B4", "4" = "#FF7F0E")) + 
  labs(x = NULL,
       y = "WT RBD ELISA (OD value)",
       caption = "1 Dose") +  
  theme_bw(base_size = 12) +  
    theme(plot.caption = element_text(face = "bold", size = 10, hjust = 0.5),
        plot.title = element_text(face = "bold", size = 14),
        axis.title = element_text(face = "bold"),
        axis.text.x = element_text(angle = 0, hjust = 0.5, vjust = 0.5, face = "bold"),  
        panel.grid.major = element_blank(),  
        panel.grid.minor = element_blank(),  
        axis.ticks = element_line(),  
        legend.position = "none",
        panel.border = element_blank(),
        axis.line = element_line(size = 0.5, color = "black", linetype = "solid")
  )

one_elisa_wt_plot
```

#TWO
```{r}
two_elisa_wt <- fc_perm_summary(two_dose_data, two_dose_permutation, v2_elisa_wt, min_n = 5, dose_label = "2 Dose")

two_valid_perms_e      <- two_elisa_wt$valid_perms
two_dose_medians_e     <- two_elisa_wt$medians
two_n_levels_e         <- two_elisa_wt$n_levels
two_mid_x_e            <- two_elisa_wt$mid_x

print(two_elisa_wt$valid_perm_count)
```

```{r}
two_labels <- c("1-1" =" B-B", "4-4" ="S-S")

response_colq <- "v2_elisa_wt"

two_elisa_wt_plot <- ggplot() +
  geom_jitter(data = two_valid_perms_e,
              aes_string(x = "two_dose_permutation", y = response_colq, color = "two_dose_permutation"),
              alpha = 0.8, width = 0.18, size = 2.5) +
  geom_crossbar(data = two_dose_medians_e,
                aes_string(x = "two_dose_permutation", y = "median",  
                           ymin = "median", ymax = "median"),  
                width = 0.5, colour = "black", size = 0.5) +  
  scale_x_discrete(labels = two_labels, limits = c("1-1","4-4"), expand = expansion(add = c(0.5, 0.5))) +
  scale_y_continuous(limits = c(0, 6), breaks = seq(0, 6, by = 0.5)) +
  scale_color_manual(values = c("1-1" = "#1F77B4", "4-4" = "#FF7F0E")) + 
  labs(x = NULL,
       y = "WT RBD ELISA (OD value)",
       caption = "2 Doses") +  
  theme_bw(base_size = 12) +  
    theme(plot.caption = element_text(face = "bold", size = 10, hjust = 0.5),
        plot.title = element_text(face = "bold", size = 14),
        axis.title = element_text(face = "bold"),
        axis.text.x = element_text(angle = 0, hjust = 0.5, vjust = 0.5, face = "bold"),  
        panel.grid.major = element_blank(),  
        panel.grid.minor = element_blank(),  
        axis.ticks = element_line(),  
        legend.position = "none",
        panel.border = element_blank(),
        axis.line = element_line(size = 0.5, color = "black", linetype = "solid")
  )

two_elisa_wt_plot
```

#THREE
```{r}
three_elisa_wt <- fc_perm_summary(three_dose_data, three_dose_permutation, v3_elisa_wt, min_n = 5, dose_label = "3 Dose")

three_valid_perms_e      <- three_elisa_wt$valid_perms
three_dose_medians_e     <- three_elisa_wt$medians
three_n_levels_e         <- three_elisa_wt$n_levels
three_mid_x_e            <- three_elisa_wt$mid_x

print(three_elisa_wt$valid_perm_count)
```

```{r}
three_labels <- c("4-4-1" ="S-S-B", "4-4-4" ="S-S-S", "1-1-1" = "B-B-B")

response_colq <- "v3_elisa_wt"

three_elisa_wt_plot <- ggplot() +
  geom_jitter(data = three_valid_perms_e,
              aes_string(x = "three_dose_permutation", y = response_colq, color = "three_dose_permutation"),
              alpha = 0.8, width = 0.18, size = 2.5) +
  geom_crossbar(data = three_dose_medians_e,
                aes_string(x = "three_dose_permutation", y = "median",  
                           ymin = "median", ymax = "median"),  
                width = 0.5, colour = "black", size = 0.5) +  
  scale_x_discrete(labels = three_labels, limits = c("1-1-1", "4-4-4", "4-4-1"), expand = expansion(add = c(0.5, 0.5))) +
  scale_y_continuous(limits = c(0, 6), breaks = seq(0, 6, by = 0.5)) +
  scale_color_manual(values = c("1-1-1" = "#1F77B4", "4-4-4" = "#FF7F0E", "4-4-1" = "#1B5E20", "1-1-4" = "#4A148C")) + 
  labs(x = NULL,  
       y = "WT RBD ELISA (OD value)",
       caption = "3 Doses") +  
  theme_bw(base_size = 12) +  
    theme(plot.caption = element_text(face = "bold", size = 10, hjust = 0.5),
        plot.title = element_text(face = "bold", size = 14),
        axis.title = element_text(face = "bold"),
        axis.text.x = element_text(angle = 0, hjust = 0.5, vjust = 0.5, face = "bold"),  
        panel.grid.major = element_blank(),  
        panel.grid.minor = element_blank(),  
        axis.ticks = element_line(),  
        legend.position = "none",
        panel.border = element_blank(),
        axis.line = element_line(size = 0.5, color = "black", linetype = "solid")
  )

three_elisa_wt_plot
```



##PANELS 
```{r}
y_limits <- c(0, 6) 

elisa_baseline_wt <- elisa_baseline_wt + scale_y_continuous(limits = y_limits, breaks = seq(0, 6, by = 0.5)) +
  labs(y = "WT RBD ELISA (OD value)") + 
  theme(axis.text.y = element_text(size = 10), 
        axis.ticks.y = element_line(),          
        axis.line.y = element_line())  

post_infection_elisa <- post_infection_elisa + scale_y_continuous(limits = y_limits, breaks = seq(0, 6, by = 0.5)) +
  labs(y = NULL) +  
  theme(axis.text.y = element_blank(),  
        axis.ticks.y = element_blank(),  
        axis.line.y = element_blank())

one_elisa_wt_plot <- one_elisa_wt_plot + 
 scale_y_continuous(limits = y_limits, breaks = seq(0, 6, by = 0.5)) +
  labs(y = NULL) +  
  theme(axis.text.y = element_blank(),  
        axis.ticks.y = element_blank(),  
        axis.line.y = element_blank())         

two_elisa_wt_plot <- two_elisa_wt_plot + 
  scale_y_continuous(limits = y_limits, breaks = seq(0, 6, by = 0.5)) +
  labs(y = NULL) +  
  theme(axis.text.y = element_blank(),  
        axis.ticks.y = element_blank(),  
        axis.line.y = element_blank())   

three_elisa_wt_plot <- three_elisa_wt_plot + 
  scale_y_continuous(limits = y_limits, breaks = seq(0, 6, by = 0.5)) +
  labs(y = NULL) + 
  theme(axis.text.y = element_blank(), 
        axis.ticks.y = element_blank(), 
        axis.line.y = element_blank())

elisa_wt_combined_plot <- (elisa_baseline_wt + post_infection_elisa + one_elisa_wt_plot + 
                         two_elisa_wt_plot + 
                         three_elisa_wt_plot) + 
  plot_layout(ncol = 5) + 
  plot_annotation(title = "WT RBD ELISA", 
                  theme = theme(plot.title = element_text(face = "bold", size = 16, hjust = 0.5))) + 
  theme(plot.background = element_blank(),
        panel.border = element_blank(),    
        plot.margin = margin(0, 0, 0, 0))

print(elisa_wt_combined_plot)

ggsave("elisa_wt_combined_plot.pdf", plot = elisa_wt_combined_plot, width = 20, height = 6)
```



#Instructions
```{r}
# HCW immunoassay plots - SAMPLE
# - Ancestral (Wuhan) vs Omicron RBD ELISA
# Author: Wey Wen Lim
# Date: September 30, 2022
# Last updated: September 30, 2022

# Load data ----
# **NOTE: THIS PLOTTING DATASET IS PRE-PROCESSED FROM THE DATASET AVAILABLE IN THE DATA FOLDER:
# STEPS:
# 1. Identify baseline samples from biannual sampling rounds (we call it "routine" for short and use the pre-fix r1..11) - vaccines came in around mid-r2
# 2. Group participants into groups based on their vaccination history 
#    (e.g., for baseline levels, based on participants who eventually got the mRNA (by BioNTech, B) or inactivated (by SinoVac, S) vaccine as their first two doses,
#     for dose 1-4, combine information from each doseX_brand variable, 1-1-1 = B-B-B, 4-4-4 = S-S-S, 1-1-4 = B-B-S, 4-4-1 = S-S-B and so on. 
#     Am open to suggestions to change this labelling system to better ones)
# 3. Plot antibody levels 21-42 days after each dose - this doesn't need to be limited to post-vaccination samples. Some "routine" samples also fall within this time frame
# 4. For participants with antibody levels in step 3, identify a later sample (routine if possible) to plot the waning patterns

# Script ends ----

```

